---
title: "kolada"
author: "Group 19"
date: "05/10/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{kolada}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

## Package lab5
This is the package that download data from kolada using its API. 

## Install package
```{r }
devtools::install_github("spirosdim/advR_lab5", subdir="lab5")
```
## Create object
```{r }
a <- kolada$new()
```

## Methods in the class

### get_municipality_list: Get the list of municipalities in kolada
```{r }
a$get_municipality_list()
```

### get_id: Get the id of a particular municipality
Input: The name of the municipality
```{r }
a$get_id('Linköping')
```

### get_skola: Get the list of schools in a particular municipality
Input: The name of the municipality
```{r }
a$get_skola('Linköping')
```

### get_stats: Get the statistics from the kolada with given option
Input: Mname: The name of the municipality
op: Option for the statistics. 1: Death number. 2: Net numbers moving residents. 3: Born numbers per 1000 residents. 4: Born numbers.
```{r }
a$get_stats('Linköping',2)
```